---
title: "Show cellline variance on graph"
author: "Attila Gabor"
date: "3/8/2019"
output: html_document
---

```{r}
library(tidyverse)
```

## Data import
```{r}
rm(list = ls())

par_global_estimability = readRDS("./data/models/pkn_v4_midas_v4/parameter_variance/par_global_estimability.RDS")
par_stats = readRDS("./data/models/pkn_v4_midas_v4/par_stats.RDS")
par_global_variation = readRDS("./data/models/pkn_v4_midas_v4/parameter_variance/par_global_variation.RDS")
#sampling_df_qc = readRDS("./data/models/pkn_v4_midas_v4/parameter_samplings_QC.RDS")

par_stats
par_global_estimability
par_global_variation
# sampling_df_qc
```

# 
filtering out parameters with inaccurate estimation (high CL_cov))
```{r}
# using fixed threshold
par_stats = par_stats %>% mutate(accurate = CL_cov < 0.1)
par_stats
```


## Graph

### Individual cell lines
CC1806, T47D, MDAMB361 and MDAMB415
export the graph of these cell-lines to csv file to be imported in Cytoscape

```{r}
cell_lines = c("HCC1806", "T47D", "MDAMB361","MDAMB415")
for(icl in seq_along(cell_lines)){
	# icl = 1
	edge_to_export = par_stats %>% 
		filter(cell_line == cell_lines[[icl]]) %>%
		filter(grepl("_k_",parameter)) %>%
		separate(parameter,c("from","to"),"_k_", remove = FALSE)
	write.csv(edge_to_export,paste0("./supp_info/results_for_april_2019/data/par_stats_",cell_lines[[icl]],".csv"),quote = F)
}
```

Some statistics about the values that we want to show on the graph
This is used to setup the range of the mappings in cytoscape style
```{r}
par_stats %>% 
	filter(cell_line %in% cell_lines) %>%
	filter(grepl("_k_",parameter)) %>%
	summarise(median_range_L = range(CL_median)[[1]],
			  median_range_U = range(CL_median)[[2]],
			  cov_range_L=range(CL_cov)[[1]],
			  cov_range_U=range(CL_cov)[[2]])

```


The problem with above is the hierarchic layout is changing for each imported file...
One workaround is to export just 1 graph and export the cell-line specific features
by columns. Then we manually change the style in cytoscape for each cell-line. 

```{r}
	# icl = 1
edge_to_export = par_stats %>% 
		filter(cell_line %in% cell_lines) %>%
		filter(grepl("_k_",parameter)) %>%
		separate(parameter,c("from","to"),"_k_", remove = FALSE)

CL_mean = edge_to_export %>% group_by(cell_line,parameter,from,to) %>% summarise(CL_mean=CL_mean) %>% spread(key = cell_line,CL_mean)
name_map = cell_lines
names(name_map) = paste("CL_mean",cell_lines,sep="_")
CL_mean <- CL_mean %>% rename(!!name_map)

CL_cov = edge_to_export %>% group_by(cell_line,parameter,from,to) %>% summarise(CL_cov=CL_cov) %>% spread(key = cell_line,CL_cov)
name_map = cell_lines
names(name_map) = paste("CL_cov",cell_lines,sep="_")
CL_cov <- CL_cov %>% rename(!!name_map)

multi_edge_export = left_join(CL_mean,CL_cov)

write.csv(multi_edge_export,paste0("./supp_info/results_for_april_2019/data/par_stats_4_celllines.csv"),quote = F)

```

### Plotting 2 networks at the same time ----
"MDAMB361","MDAMB415"
```{r}
cell_lines_pairs = list(c("HCC1806", "T47D"),
						c("HCC1806", "MDAMB415"),
						c("HCC1806", "MDAMB361"),
						c("MDAMB361", "T47D"))
par_stats$parameter = as.character(par_stats$parameter)

for(cl_pairs in cell_lines_pairs){
	edge_to_export = par_stats %>% 
		filter(cell_line %in% cl_pairs) %>%
		filter(grepl("_k_",parameter)) %>% arrange(parameter)%>%
		separate(parameter,c("from","to"),"_k_", remove = FALSE)
	
}	
	write.csv(edge_to_export,paste0("./supp_info/results_for_april_2019/data/par_stats_",paste0(paste(cell_lines,collapse = "_vs_"),".csv")),quote = F)


```



# R2Cytoscape
Can we do the above by calling cytoscape from R?


```{r}
cell_lines = c("HCC1806", "T47D", "MDAMB361","MDAMB415")
for(icl in seq_along(cell_lines)){
	# icl = 1
	edge_to_export = par_stats %>% 
		filter(cell_line == cell_lines[[icl]]) %>%
		filter(grepl("_k_",parameter)) %>%
		separate(parameter,c("from","to"),"_k_", remove = FALSE)
	write.csv(edge_to_export,paste0("./supp_info/results_for_april_2019/data/par_stats_",cell_lines[[icl]],".csv"),quote = F)
}
```
```{r}
library("RCy3")
cytoscapePing()

```

```{r}
library(igraph)


```


```{r}

# "HCC1806"  
G = edge_to_export %>% filter(cell_line == cell_lines[[1]]) %>%
	select(-cell_line,-parameter) %>%
	graph_from_data_frame()

createNetworkFromIgraph(G,title = cell_lines[[1]])
setVisualStyle("CC_v1")
layoutNetwork(layout.name = "apply preferred")
#layoutNetwork(layout.name = "hierarchical")

setEdgeColorMapping("CL_cov",c(0,5), c('#FFFFFF','#FF7755'),style.name = "CC_v1")

# "T47D"     
G = edge_to_export %>% filter(cell_line == cell_lines[[2]]) %>%
	select(-cell_line,-parameter) %>%
	graph_from_data_frame()

createNetworkFromIgraph(G,title = cell_lines[[2]])
setVisualStyle("CC_V1_cell_line")
#layoutNetwork(layout.name = "apply preferred")
layoutNetwork(layout.name = "hierarchical")

# "MDAMB361" 
G = edge_to_export %>% filter(cell_line == cell_lines[[3]]) %>%
	select(-cell_line,-parameter) %>%
	graph_from_data_frame()

createNetworkFromIgraph(G,title = cell_lines[[3]])
setVisualStyle("CC_V1_cell_line")
#layoutNetwork(layout.name = "apply preferred")
layoutNetwork(layout.name = "hierarchical")

# "MDAMB415"
G = edge_to_export %>% filter(cell_line == cell_lines[[4]]) %>%
	select(-cell_line,-parameter) %>%
	graph_from_data_frame()

createNetworkFromIgraph(G,title = cell_lines[[4]])
setVisualStyle("CC_V1_cell_line")
# layoutNetwork(layout.name = "apply preferred")
layoutNetwork(layout.name = "hierarchical")

```

###  Show each network on the same graph ----



```{r}

# 1. arrange the cell_line data into column --> not tidy
# 1.1 nodes
nodes <-  par_stats %>% 
		filter(grepl("tau_",parameter)) %>%  # remove x0: keep only tau and k parameters
		mutate(name = gsub("tau_","",parameter))

# CL_median table for nodes:
new_names = unique(nodes$cell_line)
names(new_names) = paste0("CL_median_",new_names)
nodes_CL_median <- nodes %>%
	select(cell_line,CL_median,name) %>%
	spread(cell_line,CL_median) %>%
	rename(!!new_names)

# 1.2 edges
edges <- par_stats %>% 
	filter(grepl("_k_",parameter)) %>%
	separate(parameter,into = c("from","to"),"_k_", remove = FALSE)

# CL_median for edges: 
new_names = unique(edges$cell_line)
names(new_names) = paste0("CL_median_",new_names)
edges_CL_median <- edges %>%
	select(cell_line,parameter,from,to,CL_median) %>%
	spread(cell_line,CL_median) %>%
	rename(!!new_names)



# 2. add information on measurements and inputs
cno = CNOlist("./data/MIDAS_v4/184A1.csv")
dataNodes = colnames(cno@signals[[1]])

nodes_CL_median <- nodes_CL_median %>%
	mutate(node_type = ifelse(nodes_CL_median$name %in% dataNodes,"measured","non-measured"))

nodes_CL_median <- nodes_CL_median %>% full_join(y = data.frame(name=c("EGF","SERUM"),node_type=c("input","input"),stringsAsFactors=F),by = c("name","node_type"))


# 1. create an igraph object
G  <-  tbl_graph(nodes = data.frame(nodes_CL_median),edges = data.frame(edges_CL_median), directed = TRUE)


createNetworkFromIgraph(G,title = cell_lines[[1]])
setVisualStyle("CC_v1")
layoutNetwork(layout.name = "apply preferred")
#layoutNetwork(layout.name = "hierarchical")

cols = RColorBrewer::brewer.pal(3,"Reds")
#edge_cols = RColorBrewer::brewer.pal(3,"Set1")
cell_lines = unique(par_stats$cell_line)

for(i_celline in 1:length(cell_lines)){
	cl_name = cell_lines[[i_celline]]
	print(cl_name)
	
	var_name = paste0("CL_median_",cl_name)
	setEdgeColorMapping(var_name,c(0,1,5),cols,style.name = "CC_v1"); Sys.sleep(0.1)
	setNodeColorMapping(var_name,c(0,1,5),cols,style.name = "CC_v1"); Sys.sleep(0.1)
	setEdgeLineWidthMapping(var_name,c(0,5),widths = c(2,20),style.name = "CC_v1"); Sys.sleep(0.1)
	#setNodeBorderColorMapping("node_type",table.column.values = c("non-measured","measured","input"),colors = edge_cols,style.name = "CC_v1",mapping.type = "d"); Sys.sleep(0.1)
	
	layoutNetwork(layout.name = "apply preferred"); Sys.sleep(0.3)
	
	exportImage(filename = file.path(getwd(),"supp_info/results_for_april_2019/figures",paste0(var_name,".pdf")),type = "PDF")
	
}

# mvp <- mapVisualProperty(visual.prop = "Node Border Line Type",
# 						 table.column = "node_type",
# 						 mapping.type = "d",
# 						 table.column.values = c("non-measured","measured","input"),
# 						 visual.prop.values = c("Dots","Solid","Solid"))
# 
# mvp <- mapVisualProperty(visual.prop = "NODE_BORDER_LINE_TYPE",
# 						 table.column = "node_type",
# 						 mapping.type = "d",
# 						 table.column.values = c("non-measured","measured","input"),
# 						 visual.prop.values = c("Dots","Solid","Solid"))
# 
# # 
# updateStyleMapping("CC_v1", mvp)


```




```{r}

g = out$graph

edges = names(out$edgeAttrs$color)
nodePairs = strsplit(edges,split = "~") 
edgeStart = unlist(lapply(nodePairs,function(x)x[[1]]))
edgeEnd = unlist(lapply(nodePairs,function(x)x[[2]]))

g = initEdgeAttribute(graph = g,
					  attribute.name = "weight",
					  attribute.type = "numeric",
					  default.value = 1)

g = initEdgeAttribute(graph = g,
					  attribute.name = "edgeColor",
					  attribute.type = "char",
					  default.value = "white")

edgeData(g,from =edgeStart,to = edgeEnd ,attr = "edgeColor") <- out$edgeAttrs$color



g = initNodeAttribute(graph = g,
					  attribute.name = "label",
					  attribute.type = "char",
					  default.value = "undefined")

nodeData(g,names(nodeData(g)),"label") <- names(nodeData(g))


g = initNodeAttribute(graph = g,
					  attribute.name = "nodeFillColor",
					  attribute.type = "char",
					  default.value = "white")

nodeData(g,names(out$nodeAttrs$fillcolor),attr = "nodeFillColor") <- out$nodeAttrs$fillcolor

g = initNodeAttribute(graph = g,
					  attribute.name = "nodeColor",
					  attribute.type = "char",
					  default.value = "white")

nodeData(g,names(out$nodeAttrs$color),attr = "nodeColor") <- out$nodeAttrs$color




cw <- CytoscapeWindow ('vignette', graph=g, overwrite=TRUE)
displayGraph (cw)

```





#### add edge strength
WE cannot add it because this is based on combined edges and by parameters!!!
```{r}
edge_str = readRDS("./data/models/pkn_v4_midas_v4/features/feature_table_2_3_full_timecourse_edge_strength.RDS")
edge_str %>% as_tibble() %>% 
	gather(edges, value, contains("=")) %>%  # long format
	group_by(cell_line,edges) %>% summarise(mean_str = mean(value),  # summarise over time and treatment
											median_str = median(value)) %>%
	filter(cell_line %in% cell_lines)
```








## Global graph
```{r}
# compute statistics over all cell lines

global_stats <- par_stats %>% group_by(parameter) %>% filter(accurate,.preserve = T) %>%
	summarise(CoV_par = sd(CL_mean)/mean(CL_mean), n_celline = sum(accurate))
global_stats

global_stats$CoV_par[is.na(global_stats$CoV_par)] = 0
global_stats
```



```{r}
edges_stats <- global_stats %>%
	filter(grepl("_k_",parameter)) %>%
	separate(parameter,c("from","to"),"_k_", remove = FALSE)
edges_stats
```

```{r}
write.csv(edges_stats,"./supp_info/results_for_march_2019/data/par_stats_v1.csv",quote = F)
```

write node annotation table: non-measured nodes initial condition are estimated
```{r}
non_measured_nodes = c("EGF","SERUM",gsub("x0.","",grep("x0",global_stats$parameter,value = T),fixed = T))
all_nodes = unique(c(edges_stats$from,edges_stats$to))
node_table = data_frame(node=all_nodes)
node_table <- node_table %>% mutate(node_type = ifelse(node%in%non_measured_nodes,"non-measured","measured"))
node_table
```


```{r}
write.csv(node_table,"./supp_info/results_for_march_2019/data/par_stats_v1_nodes.csv",quote = F)
```

this is continued in Cytoscape. 


